The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
nobs results

Larger landcover resolution scale resulted in decreased proportion of rare and
patchy habitats and low connectivity of individuals in these habitats. In
winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure 3c). Connective redundancy decreased with increasing
landcover resolution due the decrease in connectivity of individuals in winter
forage habitats, resulting in a multilayer network where neighbours were less
frequently repeated in multiple layers (Figure 3b). Layer similarity was
generally stable for forest and open habitats except for a contrasting increase
in similarity for forest and decrease in similarity for open habitats at 250m
landcover resolution (Figure 3a). Layer similarity was not possible to calculate
between winter and summer forage because, at all landcover resolutions greater
than 10m there were no individuals connected in the network layers. <!--
individuals still used forage but in much lower proportion + lowered opportunity
to associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.

@@

>>>>

Larger landcover resolution scale resulted in decreased proportion of rare and
patchy habitats and low connectivity of individuals in these habitats. In
winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure 4c). Connective redundancy decreased with increasing
landcover resolution due the decrease in connectivity of individuals in winter
forage habitats, resulting in a multilayer network where neighbours were less
frequently repeated in multiple layers (Figure 4b). Layer similarity was
generally stable for forest and open habitats except for a contrasting increase
in similarity for forest and decrease in similarity for open habitats at 250m
landcover resolution (Figure 4a). Layer similarity was not possible to calculate
between winter and summer forage because, at all landcover resolutions greater
than 10m there were no individuals connected in the network layers. <!--
individuals still used forage but in much lower proportion + lowered opportunity
to associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low number of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below ~75 observations for forest, ~210 observations for open
and ~300 observations for forage (Figure 5a). Once sufficient observations were
used, layer similarity stabilized with additional for all three landcover
classes at ~200 observations for forest, ~300 observations for open and forage.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure 5b).
Given the overall trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing the social dynamics across contexts.
